Introduction to Natural Language Processing

### 2007-07-12 slides/baypiggies.tex
slide updates
svn/trunk@4876

\documentclass{beamer}             % for slides
\usepackage{alltt}
% \documentclass[handout]{beamer}    % for handout
\input{beamer}

@@

\begin{frame}
  \frametitle{Natural Language Processing}
  \begin{itemize}
    \item text and information
      \note[item]{world is awash with text; information locked up in text}
      \note[item]{sources: news, blogs, transcribed speech, other languages}
    \item Natural Language Processing (NLP)
      \note[item]{automatically process text, extracting structure and content, to give people access to the information}
    \item Engineering goals
      \note[build a system to provide a service (translation, summarization)]
    \item Scientific goals
      \note[analyze the structure of language, computational linguistics]
    \item Data
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{IOB-Tagged Text (I=inside, O=outside, B=begin)}
{\scriptsize\begin{verbatim}
Characteristically RB B-ADVP
, , O
he PRP B-NP
did VBD B-VP
n't RB I-VP
waste VB I-VP
much JJ B-NP
time NN I-NP
getting VBG B-VP
started VBN I-VP
. . O
\end{verbatim}}
\end{frame}

>>>>

\documentclass{beamer}             % for slides
%\documentclass[notes,handout]{beamer} % presenter notes
% \documentclass[handout]{beamer}    % for handout
\usepackage{alltt}
\input{beamer}

@@

\begin{frame}
  \frametitle{Natural Language Processing}
  \begin{itemize}
    \item text and information
      \note[item]{world is awash with text; information locked up in text}
      \note[item]{sources: news, blogs, transcribed speech, other languages}
    \item Natural Language Processing (NLP)
      \note[item]{automatically process text, extracting structure and content, to give people access to the information}
    \item Engineering goals
      \note[item]{build a system to provide a service (translation, summarization)}
    \item Scientific goals
      \note[item]{analyze the structure of language, computational linguistics}
    \item Data
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{IOB-Tagged Text}
{\scriptsize\begin{verbatim}
Characteristically RB B-ADVP
, , O
he PRP B-NP
did VBD B-VP
n't RB I-VP
waste VB I-VP
much JJ B-NP
time NN I-NP
getting VBG B-VP
started VBN I-VP
. . O
\end{verbatim}}
\end{frame}
